Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-25 doc/PRF2022/PRF_main.tex
discussion completed; abstract added

\subsection{Mobility problem}
A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
is time. The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis. The boundary of
$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
terms are negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$. 
Without inertia, the system in \eqref{eq:stokes}-\eqref{eq:rigid-vel} also satisfies the force-free and torque-free conditions.
This means that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic stress on each particle (with subscript `$i$')
are in balance with the force and torque from the hydrophobic potential \cite{Fu2022_JFM}.
The total force and torque from the fluid flow are computed as
\begin{equation}
  \label{eq:force}
 \FF_i \equiv \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
 T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu_i) \, \dif s,
  \quad i=1,\ldots,N_b,
\end{equation}
where 
%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
%are interparticle forces and torques. 
$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor), and
$\nnu_i$ is the unit outward normal on the $i$th particle.

$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
the minimizer of the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
In the followings we use the radius of JP for $c$.

The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
We obtain
a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
With 
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.

Variation of the the free energy \eqref{eq:free_energy} provides
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress identified in ~\cite{Fu20} and derived by
variation of the domain techniques.

@@

Once the translational and angular velocities $\vv_i, \omega_i$
have been determined, a second-order Adams-Bashforth scheme updates the particle
positions and orientations:
\begin{equation}
  \label{eq:adams-bashforth}
  \begin{aligned}
    \aa_i(t_{n+2}) &=
\aa_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
    \theta_i(t_{n+2}) &=
\theta_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
  \end{aligned}
\end{equation}

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx$ and  $\aa_i$, and 
$\dd_i = (\cos \theta_i, \sin \theta_i)$ isthe particle director.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

With max$(g)>0$ to guarantee (at least partial) hydrophobic surface on each JP,  
the boundary condition can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases,
respectively. 
Case (i) with $b = 1$ (bc(i)) mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head (green),
and takes the maximum value $a$ on the
hydrophobic tail (red). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run.
Both cases form bilayers with multiple components.

In case (ii) with $b = 1$ (bc(ii)) the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

In case (iii) with $b=1$ (bc(iii))
a water structure with
positive/negative charge is possible \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. 
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
    The results of the striated configuration, however, depend on the initial geometrical setup.
  }
\end{figure}

@@

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of the total particle number $(N_b)$.

@@

We must modify $S_2$ to account for the bilayer and
multilamellar structures.  In these cases, the directors 
are more or less bilayer uniformly distributed along a circle, even though
there is orientational order between neighboring particles.
To account for local order, we instead use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

Figure~\ref{fig:relax_energy}(b) 
tracks the orientational order parameter $\tilde{S}_2$.
Both bilayer and multilamellar
structures show similar trends in the small and large particle number systems
(Figure \ref{fig:relax}(b) black curves, red curves respectively).
The multilamellar structures are highly ordered in all cases (Figure~\ref{fig:relax}(c))
whereas the bilayer structures
are disordered because they consist of several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).

The aggregation for striated configurations form more than one 
pattern when the number of particles is varied (Figure~\ref{fig:relax}(d)).
We observe that when the number of particles is fewer, there is only
a single alternating pattern in particle orientations where the directors
are more or less parallel and alternate directions between stria (Figure~\ref{fig:relax}(d), inset).
Larger number of particles results in two different patterns: the alternating sign pattern
as in the small particle number case (Figure~\ref{fig:relax}(d), 
top right rectangle) and one where the directors reflect across the lines parallel
to the stria and across the lines perpendicular to the stria (Figure~\ref{fig:relax}(d),
top middle rectangle).
As a result, there are different trends in orientational order
(Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).

In the Results section,
the equilibrium configurations for cases (i), (ii), and (iii)
(Figure~\ref{fig:relax}, insets) are
used as initial data in the
background flow simulations. 
For the bilayer case (i), we include an alternate initial condition 
consisting of a single, circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
    with shear flow rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
    The initial configuration is shown in inset of panel (a).
    The streamlines are plotted in the background.
    Panel (d) plots the free energies,
    panel (e) shows the orientational parameter $\tilde{S}_2$,
    and panel (f) shows positional parameter E.
}
\end{figure}

@@

\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
under a linear shear flow.
At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, 
similar to the asymmetric breakup of a viscous drop \cite{}.
In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two separate, nearly equal bilayers, 
similar to the symmetric drop breakup under a linear shear flow \cite{}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

In terms of deformation measures,  
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  
Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.

An interesting feature of the simulations is that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
is on average increasing.  In the initial configuration,
the structure has three or four components.  
%
Under the shear flow, the shedding and merging of bilayers
result in an overall decrease in distinct bilayer structures.  
This suggests that
the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.   
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

>>>>

\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent.
The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
and $N_b$ is the number of particles.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
is time.  The boundary of
$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
terms are negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
This means that the force and torque from the hydrodynamic stress on each particle 
are in balance with the total
force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
To compute this balance, we define
the free energy\cite{Fu2022_JFM}
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
where $u(\xx,t)$ is as an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
The parameter $\rho_0$ is an ``effective" distance between particle centers,
below which the steric repulsion between a pair of JPs becomes important.

The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
Its governing equations $u(\xx,t)$ 
are a screened Laplace equation boundary value problem
as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.

To get forces and torques from the free energy,
we compute the variation of the domain of the free energy 
\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
and obtain 
\begin{equation}
  \FF_i \equiv \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress.
Repulsion is rotationally symmetric and does not contribute to the torque.
The derivation details are found in \citet{Fu20}.

Since the force and torque from the hydrodynamic stress on each particle
are in balance with the total force and torque coming from the
hydrophobic potential and repulsion, we have
\begin{equation}
  \label{eq:force}
 \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
 \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu) \, \dif s = T_i,
  \quad i=1,\ldots,N_b,
\end{equation}
where 
%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
%are interparticle forces and torques. 
$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).

@@

%Once the translational and angular velocities $\vv_i, \omega_i$
%have been determined, a second-order Adams-Bashforth scheme updates the particle
%positions and orientations:
%\begin{equation}
%  \label{eq:adams-bashforth}
%  \begin{aligned}
%    \aa_i(t_{n+2}) &=
%\aa_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
%    \theta_i(t_{n+2}) &=
%\theta_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
% \end{aligned}
%\end{equation}

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  2\pi c$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP surface.
Then, the boundary condition (BC) can be classified into
three categories: $\min g >0$, $\min g =0$, and $\min g <0$.  
These three categories correspond to three characteristic
values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Fig~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayer for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Fig~\ref{fig:relax}(a) shows the initial configurations with
orientations of the 198-particle and 60-particle cases,
respectively. 
BC (i) with $b = 1$ mimicks an amphiphilic particle.
The boundary data $g$ is everywhere nonnegative,
and takes
the maximum value $a$ on the hydrophobic tail (red)
the value $0$ on the hydrophilic head (green). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for the 60-particle run.
Both cases form bilayers with multiple components.

In BC (ii) with $b = 1$, the boundary data is everywhere positive.
It takes the maximum value $3a$ on the tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Fig~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

Finally, BC (iii) with $b=1$ 
corresponds to a water structure with
positive/negative charge \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Fig~\ref{fig:relax}(d)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Fig \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Fig \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. 
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
    The results of the striated configuration, however, depend on the initial geometrical setup.
  }
\end{figure}

@@

Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary condtions is independent of the total particle number $(N_b)$.

@@

We must modify $S_2$ to account for the bilayer and
multilamellar structures.  In these cases, the directors 
are more or less uniformly distributed along a circle, even though
there is orientational order between neighboring particles.
To account for local order, we instead use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1),
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

Fig~\ref{fig:relax_energy}(b) 
tracks the orientational order parameter $\tilde{S}_2$.
Both bilayer and multilamellar
structures show similar trends in the small and large particle number systems
(Fig \ref{fig:relax_energy}(b) black curves, red curves respectively).
The multilamellar structures are highly ordered in all cases (Fig~\ref{fig:relax}(c))
whereas the bilayer structures
are disordered because they consist of several 
components forming isolated bilayers, micelles, and vesicles (Fig~\ref{fig:relax}(b)).

The aggregation for striated configurations forms more than one 
pattern when the number of particles is varied (Fig~\ref{fig:relax}(d)).
We observe that when the number of particles is fewer, there is only
a single pattern in particle orientations where the directors
are more or less parallel and alternate directions (Fig~\ref{fig:relax}(d), inset).
Larger number of particles results in two different patterns: the alternating sign pattern
as in the small particle number case (Fig~\ref{fig:relax}(d), 
top right rectangle) and one where the directors reflect across the lines parallel
to the stria and across the lines perpendicular to the stria (Fig~\ref{fig:relax}(d),
top middle rectangle).
As a result, there are different trends in orientational order
(Fig~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).

In the Results section,
the equilibrium configurations for BCs (i), (ii), and (iii)
(Fig~\ref{fig:relax}, insets) are
used as initial data in the
background flow simulations. 
For the bilayer case BC (i), we include an alternate initial condition 
consisting of a single, circular vesicle (c.f., Fig~\ref{fig:Ves_shear}).

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
    with shear rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
    The initial configuration is shown in inset of panel (a).
    The streamlines are plotted in the background.
    Panel (d) plots the free energies,
    panel (e) shows the orientational parameter $\tilde{S}_2$,
    and panel (f) shows positional parameter E.
}
\end{figure}

@@

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of Fig~\ref{fig:relax}(b)
in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.
The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
Fig~\ref{fig:BC1_shear}(a)--(c)
shows a snapshot
at $t = 0.5$ $\upmu$s
of the bilayer for different shear rates $\dot\gamma= 0.05,0.075,0.01$.
The dynamics of the bilayer can be found in the supplementary movies,
which show that the initial pieces of bilayers merge and form a worm-like shape
under a linear shear flow.
At a low shear rate, the bilayer constantly goes through rotation and
extensional deformation with the whole bilayer remaining intact (figure~\ref{fig:BC1_shear}(a)).
As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)),
the bilayer is observed to shed a small piece of bilayer, 
similar to the asymmetric breakup of a viscous drop \cite{}.
In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two separate, nearly equal bilayers, 
similar to the symmetric drop breakup under a linear shear flow \cite{}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

We observe that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
is on average increasing.  In the initial configuration,
the structure has three or four components.  
%
Under the shear flow, the shedding and merging of bilayers
results in an overall decrease in distinct bilayer structures.  
Similarly, the free energies 
are slightly decreasing (Fig~\ref{fig:BC1_shear}(d)),
with the overall changes occuring in the range of a few $\mathrm{k_BT}$/nm.  
This suggests that
the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with lesser free energy and greater orientational order.   
Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear rate cases (Fig~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
The figure shows a single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
\end{figure}
%
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a linear shear flow. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
(such as tank-treading, bilayer slip and permeability),
our previous studies showed the existence of a critical shear
rate above which the JP vesicle ruptures. 
Based on the these early results, we
reinitialized the BC (i) configuration
in the form of a single, circular vesicle (rather than several bilayer components)
and illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.
